---
title: "Car Production"
author: "Krishna Sai Patha (s3670773)"
date: "27 October 2018"
output: word_document
---

Plotly URL:   https://plot.ly/~Patha/3/#/

Libraries:

```{r setup, include=FALSE}
library(dplyr)
library(ggplot2)
library(tidyr)
library(readr)
library(plotly)
```



```{r}
username <- "your username"
apikey <- "you apikey"
Sys.setenv("plotly_username"= username)
Sys.setenv("plotly_api_key"= apikey)
```


Dataset:

```{r }
production <- read_csv("~/Data Visualization/production.csv")
test <- data.frame(country=character(), year=integer(), value=integer(), stringsAsFactors = FALSE)
for(country in unique(production$Country)) {
  test[nrow(test)+1, ] <- list(country, 2010, production$`2010`[production$Country == country])
  test[nrow(test)+1, ] <- list(country, 2011, production$`2011`[production$Country == country])
  test[nrow(test)+1, ] <- list(country, 2012, production$`2012`[production$Country == country])
  test[nrow(test)+1, ] <- list(country, 2013, production$`2013`[production$Country == country])
  test[nrow(test)+1, ] <- list(country, 2014, production$`2014`[production$Country == country])
  test[nrow(test)+1, ] <- list(country, 2015, production$`2015`[production$Country == country])
}
View(test)
```

## Including Plots

You can also embed plots, for example:

```{r}
g <- plot_ly(data= test,x=~country,y=~value,type = "scatter",color= ~year) 

g<- g %>% layout(title="World Passenger Car Production(Selected Countries)",
                 xaxis = list(zeroline = FALSE, title="Countries"),
                yaxis = list(zeroline = FALSE, title="Thousands Of Vehicles"))
g


   api_create(g, filename = "World Passenger Car Production(Selected Countries)", sharing = "public")
```

From the plot we can see that Japan and United States being top most automobile indutries there is a huge decline in their production even though Japan has more production quantity than United States. we can also see there is a decline in Brazil also.We can also see a slighlty decline in the countries Germany,France and Australia.
