---
title: "Corruption Perception Index"
author: "Krishna Sai Patha"
date: "29 October 2018"
output: word_document
---
Data Source : 

http://www.transparency.org/cpi2015

Story(Article) URL: 

https://www.tandfonline.com/doi/full/10.1080/17449626.2014.935982


RPubs URL : http://rpubs.com/krishnasai/434576


```{r setup, include=FALSE}
library(plotly)
library(readr)

```



Plots:

Let's find which country has the highest CPI and which has the least.The bigger the numberThe Corruption Perception Index scores countries on a scale of 0-100, where 0 means that a country is perceived as highly corrupt and 100 means that a country is perceived as very clean.

```{r}
cpi <- read_csv("Data Visualization/Story Telling/cpi.csv")

l <- list(color = toRGB("grey"), width = 0.5)

# specify map projection/options
g <- list(
  showframe = FALSE,
  showcoastlines = FALSE,
  projection = list(type = 'Mercator')
)

 plot_geo(cpi) %>%
  add_trace(
    z = cpi$CPI, color =cpi$CPI, colors = 'Blues',
    text = cpi$Country, locations = cpi$Code, marker = list(line = l)
  ) %>%
  colorbar(title = 'CPI') %>%
  layout(
    title = 'Global Corruption Perception Index 2012<br>Source:<a href="http://www.transparency.org/cpi2015">CPI Data</a>Article:<a href="https://www.tandfonline.com/doi/full/10.1080/17449626.2014.935982">TandFonline</a>',
    geo = g
  )
```

We can see that New Zealand, Finland, Denmark are the cleanest countries with low corruption and Somalia is highly corrupted country.
